---
title: "Grading Multiple Choice Exams at the DPECS"
author: Test Committee
output:
  pdf_document: default
  html_document:
    df_print: paged
---

<!-- Version 2 -->

```{r, echo=FALSE}
source("linear_interpolation_grading_schema.R")
library(ggplot2)
library(knitr)

knitr::opts_chunk$set(fig.width=8, fig.height=3)

schemata <- function(n_questions, n_choices) {
  risbo = grading_schema(n_questions = n_questions,
                   guessing_score = n_questions/n_choices,
                   rounding_up_passing_score = TRUE)
  dpecs = grading_schema(n_questions = n_questions,
                   guessing_score = n_questions/n_choices,
                   rounding_up_passing_score = FALSE,
                   bilinear_interpolation = FALSE)

  return(list(risbo=risbo, dpecs=dpecs))
}

print_table <- function(n_questions, schemata) {
  df = data.frame()
  x = 1
  c = 1
  align=""
  while(TRUE) {
    scores = x:(x+19)
    scores[scores>n_questions] = NA
    df[1:20, paste0("Score", c)] = scores
    df[1:20, paste0("Grade", c)] = grades(scores, schemata$dpecs, rounding_digits = 1)
    x = x + 20
    c = c + 1
    align = paste0(align, "rll")
    if (x>n_questions) break
  }
  knitr::kable(df,  align=align, caption="Grading table")
}


dpecs_formular <- function(s) {
  rtn = "Formular: $$grade = \\begin{cases}"
  rtn = paste0(rtn, round(s$dpecs$interp_pass$const, 3), "+", round(s$dpecs$interp_pass$b, 3),
               "\\cdot score & \\text{if } score > ", round(s$dpecs$lowest_grade_breakpoint,2),
               "\\\\")
  rtn = paste0(rtn, s$dpecs$lowest_grade, " & \\text{if } score \\leq",
               round(s$dpecs$lowest_grade_breakpoint,2))
  return(paste0(rtn," \\end{cases}$$"))
}


plot_grades <- function(s) {
  points = data.frame(x=c(s$dpecs$passing_score, s$dpecs$n_questions),
                  y=c(s$dpecs$passing_grade, s$dpecs$highest_grade))
  ggplot() +
    #risbo
    geom_line(data=grading_table(s$dpecs), aes(x=score, y=grade)) +
    geom_point(data = points, aes(x,y), size=3, alpha = 0.75) +
    geom_hline(yintercept = s$dpecs$passing_grade, colour = "#999999") +
    #scale_color_manual(values=c("#CC6666", "#9999CC" )) +
    #labs(color="Method") +
    scale_y_continuous(name="Grade", breaks=s$risbo$lowest_grade:s$risbo$highest_grade) +
    xlab('Test Score') +
    theme_bw()
}
```


## Grading procedure

To calculate the grades from the scores of a multiple choices test, the DPECS uses a single linear interpolation between the point of the pass-fail criterion, $P_1$, and the highest possible grade, $P_2$. The smallest passing score has to fulfil the criterion of at least 55% knowledge, that is, 55% correct questions after guessing correction. 


For example, if we have $n=$ **40 questions with 4 choices**, the guessing correction is $c_g=40/4=10$. With a knowledge criterion $k_p=.55$ and a passing grade $g_{p}=5.5$, the passing score $s_p$ ("exact caesura") is :

$$s_p = k_p ( n - c_g) + c_g = .55\, (40 -10) + 10 = 26.5$$

Thus, if the highest possible grade is $g_{h}=10$, the interpolation uses the following two points: $$P_1 = (s_p, g_p)=(26.5,5.5)$$ $$P_2 =(n, g_h)=(40,10) $$


Find below the grading procedure of multiple choice exam often used at the DPECS.

\newpage

```{r, echo=FALSE}
n_choices = 4
n_questions = 40
s = schemata(n_questions, n_choices)
```
## MC exam with `r n_questions` questions and `r n_choices` choices
`r dpecs_formular(s)`
```{r, echo=FALSE}
plot_grades(s)
print_table(n_questions, schema = s)
```

\newpage
```{r, echo=FALSE}
n_choices = 3
n_questions = 50
s = schemata(n_questions, n_choices)
```
## MC exam with `r n_questions` questions and `r n_choices` choices
`r dpecs_formular(s)`
```{r, echo=FALSE}
plot_grades(s)
print_table(n_questions, schema = s)
```



\newpage
```{r, echo=FALSE}
n_choices = 4
n_questions = 50
s = schemata(n_questions, n_choices)
```
## MC exam with `r n_questions` questions and `r n_choices` choices
`r dpecs_formular(s)`
```{r, echo=FALSE}
plot_grades(s)
print_table(n_questions, schema = s)
```

\newpage
```{r, echo=FALSE}
n_choices = 3
n_questions = 60
s = schemata(n_questions, n_choices)
```
## MC exam with `r n_questions` questions and `r n_choices` choices
`r dpecs_formular(s)`
```{r, echo=FALSE}
plot_grades(s)
print_table(n_questions, schema = s)
```




\newpage
```{r, echo=FALSE}
n_choices = 2
n_questions = 80
s = schemata(n_questions, n_choices)
```
## MC exam with `r n_questions` questions and `r n_choices` choices
`r dpecs_formular(s)`
```{r, echo=FALSE}
plot_grades(s)
print_table(n_questions, schema = s)
```



\newpage
```{r, echo=FALSE}
n_choices = 2
n_questions = 90
s = schemata(n_questions, n_choices)
```
## MC exam with `r n_questions` questions and `r n_choices` choices
`r dpecs_formular(s)`
```{r, echo=FALSE}
plot_grades(s)
print_table(n_questions, schema = s)
```
